---
title: "Homework 6"
author: "Gavin Hyde"
date: "3/7/2022"
output: html_document
---

Loading the data
````{r}
HAPPY = readRDS("data/HAPPY.rds")
library(ggplot2)
library(dplyr)
````

Part I 

Data cleaning: the values “IAP”, “DK” and “NA” all encode missing values. Replace all of these instances by the value NA.
````{r}
HAPPY <- replace(HAPPY, HAPPY == "IAP", NA)
HAPPY <- replace(HAPPY, HAPPY == "DK", NA)
HAPPY <- replace(HAPPY, HAPPY == "NA", NA)
````


Check the type of the variable and cast into the right type (factor variable for categorical variables). For age, change “89 OR OLDER” to 89 and assume the variable should be numeric.
````{r}
HAPPY <- HAPPY %>% mutate(
  age = replace(AGE, AGE == "89 AND OLDER", 89),
  age = as.numeric(age)
) %>% select(-AGE)
````

Bringing levels of factors to a sensible order
````{r}
HAPPY <- HAPPY %>% mutate(
  degree = factor(tolower(DEGREE)),
  degree = factor(degree, levels=c("lt high school", "high school", "junior college", "bachelor", "graduate school"))
) %>% select(-DEGREE)
````

Part II

Personal Exploration- Gavin Hyde

````{r}
HAPPY %>% ggplot(aes(x=MARITAL,fill=HAPPY)) + 
  geom_bar() + 
  facet_wrap(~FINRELA) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
````

Part III
1. Gavin Hyde
My usual partner said that he had already completed the assignment on his own, I didn't know who else to ask to be my partner, so I just did the same. I still pushed to the repository.
2. https://github.com/hyde-gavin/homework6.git